\vspace{-2cm}Formation Control of AAUSHIP

### 2015-04-12 paper.tex
JAL: Author affiliation added

%\newacronym{FRP}{FRP}{Formation Reference Point}
%\newacronym{GNC}{GNC}{Guidance, Navigation and Control}
%\newacronym{LOS}{LOS}{Line-Of-Sight}
\title{\vspace{-2cm}Formation Control of AAUSHIP}
\author{Nick Østergaard \and Jeppe Dam \and Jesper A. Larsen}
\maketitle

%\begin{center}
%\vspace{-0.7cm}
%Group 12gr730
%\end{center}
%\thispagestyle{empty}

@@

The algorithm generating this combined agent can be seen in pseudo
code in algorithm \ref{al:clusteragents}.
\begin{algorithm}[h]
  \KwData{clustering of agents}
  initialization\;
  \If{$||\mathbf{p}_i , \mathbf{p}_j|| < 2 \cdot r$}{
  $\mathbf{p}_{j,new} \gets \text{mid point between}\ \mathbf{p}_i\ \text{and}\ \mathbf{p}_j$\\
  $r_{new} \gets \text{calc new r for}\ \mathbf{p}_{j,new}$\\
  delete $\mathbf{p}_i\ \text{and}\ \mathbf{p}_j \text{with}\ \mathbf{p}_{j,new}$
  }
	\caption{This pseudo code describes how agents that are too close to
		each other are getting clustered and seen as one. The algorithm
		can also be applied for obstacles in the potential
		field.\vspace{3mm}}
  \label{al:clusteragents}
\end{algorithm}

The algorithm works by first checking every distance between the agents to see if it is lower
than $2 \cdot r$. If the distance is lower, a new coordinate set needs
to be calculated. The coordinates for the $\mathbf{p}_{j,new}$ is
generated to the middle value of the two points
\begin{align}
\mathbf{p}_{j,new} = \frac{\mathbf{p}_i + \mathbf{p}_j}{2}
\end{align}
and afterwards the new radius for $\mathbf{p}_{j,new}$ can be found from
\begin{align}
r_{new} = \frac{||\mathbf{p}_i , \mathbf{p}_j||}{2} + r
\end{align}

@@

\begin{algorithm}[h]
	\KwData{track as global mission trajectory as way points}
	initialization\;
	\While{$m <=$ length of track}{
		\For{every $i$-th boat}{
			\If{formation is ok}{
				\If{$\mathbf{p}_{vl}$ is inside the way point acceptance radius of the
				track}{
					$m \gets m + 1$\; 
					$\mathbf{p}_{vl} \gets$ \textsl{LOS}$(\ p_{vl}\ ,\ $track($m$)\ )\;
				}
			}
			$(\ \mathbf{p}_{d,i}\ ,\ \mathbf{F}_{\text{tot},i}\ ) \gets $  \textsl{pathgen}(\ $p_i$\ ,\ $p0_i$\ )\;
			$\mathbf{p}_{r,i} \gets \mathbf{p}_i + \mathbf{F}_{\text{tot},i}$\;
			$\psi_{d,i} \gets $ heading from $\mathbf{p}_i$ to $\mathbf{p}_d$\;
			$u_i \gets $ \textsl{controller}(\ $\psi_d$\ )\;
			\textsl{send input $u$ to ship}\;
			$\mathbf{x}_i \gets $ \textsl{sense ship states}\;
			$\mathbf{p}_i \gets $ position of $\mathbf{x}_i$\; 
		}
	}
	\caption{This pseudo code describes how the potential field is used
	for each boat to calculate the reference for the inner controller
	for every boat at every time step. Every iteration in the while loop
	is a time step.\vspace{6pt}}
	\label{al:potfield}
\end{algorithm}

@@

%As the complete
%conclusion should the tests be performed in the same location of
%interest as the data have been taken by the Port of Aalborg. The
%conclusion should by that time be that the fleet can do it as good as
%the manual scanning performed by The Port of Aalborg.

\bibliographystyle{apalike} 
\bibliography{bib}
\end{document}

>>>>

%\newacronym{FRP}{FRP}{Formation Reference Point}
%\newacronym{GNC}{GNC}{Guidance, Navigation and Control}
%\newacronym{LOS}{LOS}{Line-Of-Sight}
\title{\vspace{-2cm}Formation Control of AAUSHIP}
%\author{Nick Østergaard \and Jeppe Dam \and Jesper A. Larsen}
\author{\IEEEauthorblockN{Nick Østergaard}
\IEEEauthorblockA{Dep. of Electronic Systems\\Aalborg University\\Denmark} 
\and
\IEEEauthorblockN{Jeppe Dam}
\IEEEauthorblockA{Dep. of Electronic Systems\\Aalborg University\\Denmark}
\and
\IEEEauthorblockN{Jesper A. Larsen}
\IEEEauthorblockA{Dep. of Electronic Systems\\Aalborg University\\Denmark\\Email: jal@es.aau.dk}

}
\maketitle

@@

\begin{algorithm}[h]
  \KwData{clustering of agents}
  initialization\;
  \If{$||\mathbf{p}_i , \mathbf{p}_j|| < 2 \cdot r$}{
  $\mathbf{p}_{j,new} \gets \text{mid point between}\ \mathbf{p}_i\ \text{and}\ \mathbf{p}_j$\\
  $r_{new} \gets \text{calc new r for}\ \mathbf{p}_{j,new}$\\
  delete $\mathbf{p}_i\ \text{and}\ \mathbf{p}_j \text{with}\ \mathbf{p}_{j,new}$
  }
	\caption{This pseudo code describes how agents that are too close to
		each other are getting clustered and seen as one. The algorithm
		can also be applied for obstacles in the potential
		field.}
  \label{al:clusteragents}
\end{algorithm}

The algorithm generating this combined agent can be seen in pseudo
code in algorithm \ref{al:clusteragents}.
The algorithm works by first checking every distance between the agents to see if it is lower
than $2 \cdot r$. If the distance is lower, a new coordinate set needs
to be calculated. The coordinates for the $\mathbf{p}_{j,new}$ is
generated to the middle value of the two points
\begin{align}
\mathbf{p}_{j,new} = \frac{\mathbf{p}_i + \mathbf{p}_j}{2}
\end{align}
and afterwards the new radius for $\mathbf{p}_{j,new}$ can be found from
\begin{align}
r_{new} = \frac{||\mathbf{p}_i , \mathbf{p}_j||}{2} + r
\end{align}

@@

\begin{algorithm}[h]
	\KwData{track as global mission trajectory as way points}
	initialization\;
	\While{$m <=$ length of track}{
		\For{every $i$-th boat}{
			\If{formation is ok}{
				\If{$\mathbf{p}_{vl}$ is inside the way point acceptance radius of the
				track}{
					$m \gets m + 1$\; 
					$\mathbf{p}_{vl} \gets$ \textsl{LOS}$(\ p_{vl}\ ,\ $track($m$)\ )\;
				}
			}
			$(\ \mathbf{p}_{d,i}\ ,\ \mathbf{F}_{\text{tot},i}\ ) \gets $  \textsl{pathgen}(\ $p_i$\ ,\ $p0_i$\ )\;
			$\mathbf{p}_{r,i} \gets \mathbf{p}_i + \mathbf{F}_{\text{tot},i}$\;
			$\psi_{d,i} \gets $ heading from $\mathbf{p}_i$ to $\mathbf{p}_d$\;
			$u_i \gets $ \textsl{controller}(\ $\psi_d$\ )\;
			\textsl{send input $u$ to ship}\;
			$\mathbf{x}_i \gets $ \textsl{sense ship states}\;
			$\mathbf{p}_i \gets $ position of $\mathbf{x}_i$\; 
		}
	}
	\caption{This pseudo code describes how the potential field is used
	for each boat to calculate the reference for the inner controller
	for every boat at every time step. Every iteration in the while loop
	is a time step.}
	\label{al:potfield}
\end{algorithm}

@@

%As the complete
%conclusion should the tests be performed in the same location of
%interest as the data have been taken by the Port of Aalborg. The
%conclusion should by that time be that the fleet can do it as good as
%the manual scanning performed by The Port of Aalborg.
\bibliographystyle{apalike} 
\bibliography{bib}
\end{document}
